Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-29 paper/gd1.tex
Ack

To improve the contrast of the stream over the background, we next cross-match
the sample to the \pans\ photometric catalog and use the photometry to further
clean the sample.
\figurename~\ref{fig:selection} (bottom right) shows the distribution of
proper-motion-selected candidate stream stars in a de-reddened \pans\
color-magnitude diagram.
\todo{Did you also cut on $phi_2$?}.
The over-plotted isochrone is from the MESA Isochrones \& Stellar Tracks (MIST;
\citealt{Dotter:2016, Choi:2016, Paxton:2011}) and represents a
$12~\textrm{Gyr}$ old population with $\feh = -1.XX$ at a distance of $XX~\kpc$.
We use this isochrone to motivate a polygonal selection in de-reddened $g-i$
color and apparent $g$-band magnitude, as visualized by the \todo{shaded} region
in the bottom right panel of \figurename~\ref{fig:selection}.

@@

All of the clearly identifiable portions of the GD-1 stream are located at high
Galactic latitudes ($b > 20^\circ$), and we therefore do not expect significant
dust extinction or variations in extinction along the stream.
\figurename~\ref{fig:sfd} shows the $V$-band extinction in the region around the
GD-1 stream, computed from the Schlegel-Finkbeiner-Davis extinction map
(\cite{Schlegel:1998}; hereafter SFD).
For stream longitudes $-60^\circ < \phi_1 < 10^\circ$ and $-1^\circ < \phi_2 <
1^\circ$, the median $V$-band extinction is $\textrm{med}\left(A_V\right) =
0.04~\mag$, and the dispersion in $A_V$ in this region is $\sigma_{A_V} \approx
0.03~\textrm{mag}$.
For longitudes $\phi_1 < -60^\circ$, as the stream approaches the Galactic disk,
dust extinction becomes more appreciable.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{sfd.pdf}
\end{center}
\caption{%
Colored background shows the $V$-band extinction, $A_V$, in the GD-1
coordinate system.
Vertical lines roughly show the extents the identified under-density (UD) and
gap.
The maximum extinction in the UD or Gap regions is $\approx$0.07 mag.
\label{fig:sfd}
}
\end{figure}

@@

@@

\subsection{Gap}
\label{sec:res_gap}

\subsection{Underdensity}
\label{sec:res_underdensity}

@@

\acknowledgements{
Gaia
Belokurov, Casey, Geha, Hogg, Johnston, Koposov, Lisanti, Schlafly, Spergel
This research was started at the NYC Gaia DR2 Workshop at the Center for Computational Astrophysics of the Flatiron Institute in 2018 April.
AB acknowledges generous support from the Institute for Theory and Computation at Harvard University.
All code used in this work and all results are available at \url{https://github.com/adrn/GD1-DR2}.
}

@@

\appendix
\section{Completeness check and scanning pattern}
\label{sec:completeness}

>>>>

To improve the contrast of the stream over the background, we next cross-match
the sample to the \pans\ photometric catalog and use the photometry to further
clean the sample.
\figurename~\ref{fig:selection} (bottom right) shows the distribution of
proper-motion-selected candidate stream stars in a de-reddened \pans\
color-magnitude diagram (CMD).
\todo{Did you also cut on $phi_2$?}.
The over-plotted isochrone is from the MESA Isochrones \& Stellar Tracks (MIST;
\citealt{Dotter:2016, Choi:2016, Paxton:2011}) and represents a
$12~\textrm{Gyr}$ old population with $\feh = -1.XX$ at a distance of $XX~\kpc$.
We use this isochrone to motivate a polygonal selection in de-reddened $g-i$
color and apparent $g$-band magnitude, as visualized by the \todo{shaded} region
in the bottom right panel of \figurename~\ref{fig:selection}.

@@

All of the clearly identifiable portions of the GD-1 stream are located at high
Galactic latitudes ($b > 20^\circ$), and we therefore do not expect significant
dust extinction or variations in extinction along the stream.
\figurename~\ref{fig:sfd-cmd} (top panel) shows the $V$-band extinction in the
region around the GD-1 stream, computed from the Schlegel-Finkbeiner-Davis
extinction map (\cite{Schlegel:1998}; hereafter SFD).
For stream longitudes $-60^\circ < \phi_1 < 10^\circ$ and $-1^\circ < \phi_2 <
1^\circ$, the median $V$-band extinction is $\textrm{med}\left(A_V\right) =
0.04~\mag$, and the dispersion in $A_V$ in this region is $\sigma_{A_V} \approx
0.03~\textrm{mag}$.
For longitudes $\phi_1 < -60^\circ$, as the stream approaches the Galactic disk,
dust extinction becomes more appreciable.

@@

@@

\todo{segue sentences...}

@@

\figurename~\ref{fig:sfd-cmd} (middle panel) again shows the proper-motion and CMD selected stream stars, with interesting features

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{sfd-cmd.pdf}
\end{center}
\caption{%
\todo{AB}
\label{fig:sfd-cmd}
}
\end{figure}

\subsection{Gaps and under-densities}
\label{sec:res_gap}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{track-and-model.pdf}
\end{center}
\caption{%
\todo{AB}
\label{fig:track-and-model}
}
\end{figure}

\subsection{Spur}
\label{sec:res_spur}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{spur.pdf}
\end{center}
\caption{%
\todo{AB}
\label{fig:spur}
}
\end{figure}

@@

\section{Conclusions}
\label{sec:conclusions}

\acknowledgements{
It is a pleasure to thank
Vasily Belokurov,
Andrew R. Casey,
Marla Geha,
David W. Hogg,
Kathryn V. Johnston,
Sergey Koposov,
Mariangela Lisanti,
Edward Schlafly,
and David N. Spergel for useful discussions and feedback.

This work has made use of data from the European Space Agency (ESA) mission {\it
Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data
Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.  This research was
started at the NYC Gaia DR2 Workshop at the Center for Computational
Astrophysics of the Flatiron Institute in 2018 April.

AB acknowledges generous support from the Institute for Theory and Computation
at Harvard University.
All code used in this work and all results are available at
\url{https://github.com/adrn/GD1-DR2}.
}

@@

\appendix
\section{Completeness and the \gaia\ scanning pattern}
\label{sec:completeness}
